INTELLIGENT SYSTEMS

### 2021-04-10 paper_6.tex
finish 6.3.4

>>>>

\subsubsection{Recursive Mask Refinement}
By combining the labels with the enhanced masks, a semantic segmentation is obtained. The purpose is to assign the category label that describes the content to the pixels belonging to the foreground. As a semantic segmentation network it was decided to use the one called \emph{DeepLab} \cite{0876055502}. This network is trained with the improved masks and has the purpose of generating more and more precise masks, without noise, which will be used as a new training set. Enhancing the mask is a recursive process that will end when the system converges to the best representation of the mask. The masks are then used as semantic labels to continue training the network.
\begin{figure}[h!]
    \centering
    \includegraphics[width = 1 \linewidth]{images/paper6/DeepLab.png}
    \centering
    \caption{The process of semantic mask generation.}
    \label{fig:semanticWork}
\end{figure}
